Distance Sampling in \proglang{R}

### 2015-12-07 paper.Rmd
first hack at abstract

---
author:
  - name: David L Miller
    affiliation: University of St Andrews
    address: >
      Centre for Research into Ecological and Environmental Modelling,
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: dave@ninepointeightone.net
    url: http://converged.yt
  - name: Eric Rexstad
    affiliation: University of St Andrews
    address: >
      Centre for Research into Ecological and Environmental Modelling,
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: Eric.Rexstad@st-andrews.ac.uk
  - name: Jeffrey L Laake
    affiliation: National Marine Mammal Laboratory
    address: >
      Alaska Fisheries Science Center
      7600 Sand Point Way N.E., Seattle, WA 98115, USA
    email: Jeff.Laake@noaa.gov
title:
  formatted: "Distance Sampling in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "Distance Sampling in R"
  # For running headers, if needed
  #short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [distance sampling, abundance estimation, line transects, point transects, "\\proglang{R}"]
  plain:     [distance sampling, abundance estimation, line transects, point transects, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{booktabs}
output: rticles::jss_article
bibliography: jstatsoft.bib
---

>>>>

---
author:
  - name: David L Miller
    affiliation: University of St Andrews
    address: >
      Centre for Research into Ecological and Environmental Modelling,
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: dave@ninepointeightone.net
    url: http://converged.yt
  - name: Eric Rexstad
    affiliation: University of St Andrews
    address: >
      Centre for Research into Ecological and Environmental Modelling,
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: Eric.Rexstad@st-andrews.ac.uk
  - name: Jeffrey L Laake
    affiliation: National Marine Mammal Laboratory
    address: >
      Alaska Fisheries Science Center
      7600 Sand Point Way N.E., Seattle, WA 98115, USA
    email: Jeff.Laake@noaa.gov
title:
  formatted: "Distance Sampling in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "Distance Sampling in R"
  # For running headers, if needed
  #short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The estimation of the abundance of biological population is an essential part of applied ecology and wildlife management. To ensure that abundance estimates are accurate, we must account for uncertain detectability of plants and animals; distance sampling is a popular method for doing this. Here we show how models for detectabilty can be fitted using the \proglang{R} package \pkg{Distance}. We also show how \pkg{Distance} can be used to calculate Horvitz-Thompson-like estimates of abundance, interfaces to other packages to provide sophisticated analyses and a migration from previous software.
keywords:
  # at least one keyword must be supplied
  formatted: [distance sampling, abundance estimation, line transects, point transects, detection functions, "\\proglang{R}"]
  plain:     [distance sampling, abundance estimation, line transects, point transects, detection functions, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{booktabs}
output: rticles::jss_article
bibliography: jstatsoft.bib
---
